A thesis draft

### 2018-09-11 draft.tex
Add introduction about VIBES project
Add 'todonotes' package and move content in the right section

@@

>>>>

\usepackage{todonotes}

@@

 Through the history of internet, many factor changed and new innovations came,
but at the end of the day a foundamental key remained: TCP/IP performance are, 
indeed, what the users unconsciously want.\todo{Idea: talk about how TCP/IP 
performes quite well in wired connections, while in wireless one, such as 
wireless/satellite, sucks ass}
